RNA-seq Analysis

### 2021-05-07 inst/analysis/rnaseq.Rmd
finish up rough draft of manuscript

```{r}
withr::with_dir(here::here(), {
  pca <- tar_read(rnaseq_pca)
  deg <- tar_read(rnaseq_different_differences)
  gsea_p <- tar_read(rnaseq_gsea_plot)
  tfea_p <- tar_read(rnaseq_tfea_plot)
})
```

@@

>>>>

```{r}
withr::with_dir(here::here(), {
  pca <- tar_read(rnaseq_pca)
  deg <- tar_read(rnaseq_different_differences)
  results <- tar_read(rnaseq_different_differences)
  gsea_res <- tar_read(rnaseq_gsea)
  gsea_p <- tar_read(rnaseq_gsea_plot)
  tfea_p <- tar_read(rnaseq_tfea_plot)
  dds <- tar_read(dds_symbols)
})
```

@@

```{r, eval = FALSE}
pathways <-
  fgsea::gmtPathways("~/Dropbox (Partners HealthCare)/msigdb_v7.2/msigdb_v7.2_GMTs/msigdb.v7.2.entrez.gmt")

df <- 
  gsea_res %>% 
  dplyr::filter(source == "HALLMARK") %>% 
  dplyr::filter(padj < 0.05) %>% 
  tidyr::unnest(leadingEdge) %>% 
  dplyr::inner_join(results, by = c("leadingEdge" = "row")) %>% 
  dplyr::group_by(pathway) %>% 
  dplyr::slice_max(order_by = stat, n = 1) %>% 
  dplyr::arrange(desc(NES))

gois <- df$symbol %>% rlang::set_names(df$pathway)

rnks <-
  results %>%
  dplyr::select(row, stat) %>%
  dplyr::arrange(stat) %>%
  tibble::deframe()

gsea_res <-
    fgsea::calcGseaStat(
      rnks,
      selectedStats = path,
      returnAllExtremes = TRUE
    )

fgsea::plotEnrichment(
  pathway = pathways[["HALLMARK_OXIDATIVE_PHOSPHORYLATION"]], 
  stats = rnks
)
```

```{r}
plot_rnaseq_goi(dds, "HIRA")
```
